paper_replication

### 2021-12-16 paper_replication.Rmd
Update paper_replication.Rmd

```{r echo=FALSE, message=FALSE, warning=FALSE}
##### Table 2 ####

@@

label(countydem$Women) = "Women"
label(countydem$White.pct) = "White"
label(countydem$Black.pct) = "Black"
label(countydem$Native.American.pct) = "Native American"
label(countydem$Asian.pct) = "Asian"
label(countydem$Hispanic.pct) = "Hispanic"
label(countydem$Median.Income) = "Median Income"
label(countydem$College.Grad.pct) = "College Graduates"
label(countydem$percentdem2008) = "Vote Democratic"

@@

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE}
```{r echo=FALSE, message=FALSE, warning=FALSE}
##### Table 2 ####

@@

@@

label(statesummarydata$Women) = "Women"
label(statesummarydata$White.pct) = "White"
label(statesummarydata$Black.pct) = "Black"
label(statesummarydata$Native.American.pct) = "Native American"
label(statesummarydata$Asian.pct) = "Asian"
label(statesummarydata$Hispanic.pct) = "Hispanic"
label(statesummarydata$Median.Income) = "Median Income"
label(statesummarydata$College.Grad.pct) = "College Graduates"
label(statesummarydata$percentdem2008) = "Vote Democratic"

units(statesummarydata$Women) = "No."
units(statesummarydata$White.pct) = "%"
units(statesummarydata$Black.pct) = "%"
units(statesummarydata$Native.American.pct) = "%"
units(statesummarydata$Asian.pct) = "%"
units(statesummarydata$Hispanic.pct) = "%"
units(statesummarydata$Median.Income) = "$"
units(statesummarydata$College.Grad.pct) = "%"
units(statesummarydata$percentdem2008) = "%"
